Implementing Real-time Transport Services over an Ossified Network

### 2016-05-21 paper.tex
Adds outline, abstract API and notes in other sections

Table \ref{tab:services} summarises the transport services required for
real-time multimedia applications.

@@

Given a transport protocol that provides the above services, how could the
API between transport and application be structured?

\todo{Stephen: outline the TCP Hollywood API, with text and a figure}

\begin{figure}
  \centering
  ...
  \caption{Outline transport API for real-time applications}
  \label{fig:api}
\end{figure}

@@

@@

The API that is exposed to applications using TCP is not visible to the
network, and can be changed. 
\todo{discuss how the API can be relaxed to allow out-of-order delivery}
\todo{discuss how the API can be modified to accept/delivery a sequence
      of messages, rather than a byte stream, and how with consistent
      segmentation at the sender and COBS framing, this can be efficient}

@@

Assuming the above is true more generally, once wider measurements have
been conducted...

here is an abstract API for real-time transport services

we can clearly layer it above UDP: the services look a lot like PR-SCTP,
and experiences with the WebRTC data channel show that this can run over
UDP and be deployed in the wild.

>>>>

Table \ref{tab:services} summarises the transport services required for
real-time multimedia applications. From this set of services, Table
\ref{tab:api} gives an outline API. As shown, the connection primitives
are the same as those of TCP. Hosts setup and teardown sockets using 
\texttt{create\_socket()} and \texttt{close\_socket()}. Servers
\texttt{bind()} to an address they wish to accept connections from, they
\texttt{listen()} on for incoming connections, and they \texttt{accept()}
an incoming connection. Clients \texttt{connect()} to a server.

The message-oriented service is exposed by the \texttt{send\_message()}
and \texttt{receive\_message()} functions. When sending messages,
applications specify a sequence number. Applications
set the receiver's play-out delay, using \texttt{set\_po\_delay()}, in
milliseconds. This is sent to the sender, for use as part of the deadline
estimation. The sender attaches a \texttt{lifetime} to each message,
which is combined with an estimate of the current round-trip-time, and the
time that the message has spent in the sending buffer, to determine if a
message will arrive within its lifetime. A message that won't arrive
within its lifetime is considered to have \emph{expired}. Applications
specify the application-level sequence number of a message they depend on
(\texttt{depends\_on}). If the message depends on a message that has
expired, then it too is considered to have expired. The partial
reliability service follows from the deadline and dependency services:
messages will be reliably transmitted until they expire.

@@

\begin{table}
  \centering
  \begin{tabular}{ll}
    \toprule
      Function & Parameters \\
    \midrule
      \texttt{create\_socket} &  \\
      \texttt{close\_socket} & \texttt{sd} -- Socket descriptor \\
    \midrule
      \texttt{bind} & \texttt{sd} -- Socket descriptor \\
                    & \texttt{addr} -- Address to bind to \\
                    & \texttt{addrlen} -- Length of \texttt{addr} \\
      \texttt{listen} & \texttt{sd} -- Socket descriptor \\
            \texttt{accept} & \texttt{sd} -- Socket descriptor \\
                    & \texttt{addr} -- Address of peer \\
                    & \texttt{addrlen} -- Length of \texttt{addr} \\
      \texttt{connect} & \texttt{addr} -- Address to connect to \\
                    & \texttt{addrlen} -- Length of \texttt{addr} \\
    \midrule
      \texttt{set\_po\_delay} & \texttt{delay} -- Playout delay (in ms) \\
    \midrule
      \texttt{send\_message} & \texttt{sd} -- Socket descriptor \\
      & \texttt{buf} -- Message data \\
      & \texttt{len} -- Length of message data \\
      & \texttt{seq\_num} -- Sequence number \\
      & \texttt{lifetime} -- Lifetime of message (in ms) \\ 
      & \texttt{depends\_on} -- \texttt{seq\_num} of dependency \\
      & \texttt{substream} -- Substream identifier \\
      \texttt{receive\_message} & \texttt{sd} -- Socket descriptor \\
      & \texttt{buf} -- Buffer for message data \\
      & \texttt{len} -- Size of \texttt{buf} \\
      & \texttt{substream} -- Substream identifier \\
    \bottomrule
  \end{tabular}
  \caption{Outline transport API for real-time applications}
  \label{tab:api}
\end{table}

@@

\todo{Other motivation for using TCP: HTTP-based streaming protocols}

@@

The API that is exposed to applications using TCP is not visible to the
network, and can be changed. Relaxing the API to enable the out-of-order
delivery of segments is trivial: segments are delivered to the application
in the order that they arrive, with their TCP sequence attached. The TCP
sequence number can be passed to the application using the existing
Berkeley sockets API, either with the received data, or using 
\texttt{getsockopt()}. Out-of-order delivery is not useful when using a 
byte-stream abstraction, and so the API should be further modified to
provide a message-oriented abstraction. The Berkeley sockets API already
supports such an abstraction for datagram protocols.

\todo{discuss how the API can be modified to accept/delivery a sequence
      of messages, rather than a byte stream, and how with consistent
      segmentation at the sender and COBS framing, this can be efficient}

@@

While further measurement studies are required to determine the
deployability of wire-visible changes to TCP (such as inconsistent
retransmissions), we have shown that we can provide all of the transport 
services needed by real-time applications, using either TCP or UDP. The
API shown in Table \ref{tab:api} is largely similar to that PR-SCTP, which
has seen real-world deployments within the WebRTC protocol, demonstrating
that we can layer these services above UDP.

However, as described in Section \ref{sec:ossification}, there are
deployability advantages to providing these services across TCP.
